Numerical Solution of Point Defect Equations by MOOSE

### 2020-12-07 examples/point_defects/article/article.tex
article-plots

  \subsection{Neutron Irradiation}
    \subsubsection{Concentrations} \hspace{10pt}
      \begin{figure}[h!]  %Neutron - 1e-6 dpa/s - %0 Bias rate
        \centering
        \subfloat{\includegraphics[scale=0.6]{interstitial_concentration_500-5000nm-neutron-0}}
        \qquad
        \subfloat{\includegraphics[scale=0.6]{vacancy_concentration_500-5000nm-neutron-0}}
        \caption{Concentration profiles for neutron irradation with 0\% Production Bias}
        \label{figure:concentrations_neutron_0_1e-6}
      \end{figure}
      \begin{figure}[h!]  %Neutron - 1e-3 dpa/s - %0 Bias rate
        \centering
        \subfloat{\includegraphics[scale=0.6]{interstitial_concentration_500-5000nm-high_neutron-0}}
        \qquad
        \subfloat{\includegraphics[scale=0.6]{vacancy_concentration_500-5000nm-high_neutron-0}}
        \caption{Concentration profiles for high dose neutron irradation with 0\% Production Bias}
        \label{figure:concentrations_neutron_0_1e-3}
      \end{figure}
      \begin{figure}[h!]  %Neutron - 1e-6 dpa/s - %5 Bias rate
        \centering
        \subfloat{\includegraphics[scale=0.6]{interstitial_concentration_500-5000nm-neutron-5}}
        \qquad
        \subfloat{\includegraphics[scale=0.6]{vacancy_concentration_500-5000nm-neutron-5}}
        \caption{Concentration profiles for neutron irradation with 5\% Production Bias}
        \label{figure:concentrations_neutron_5_1e-6}
      \end{figure}
      \begin{figure}[h!]  %Neutron - 1e-3 dpa/s - %5 Bias rate
        \centering
        \subfloat{\includegraphics[scale=0.6]{interstitial_concentration_500-5000nm-high_neutron-5}}
        \qquad
        \subfloat{\includegraphics[scale=0.6]{vacancy_concentration_500-5000nm-high_neutron-5}}
        \caption{Concentration profiles for high dose neutron irradation with 5\% Production Bias}
        \label{figure:concentrations_neutron_5_1e-3}
      \end{figure}
      \begin{figure}[h!]  %Nuetron - Vacancy Supersaturation - 5% Bias
        \centering
        \subfloat{\includegraphics[scale=0.6]{super_saturation_500-5000nm-neutron-5}}
        \qquad
        \subfloat{\includegraphics[scale=0.6]{super_saturation_500-5000nm-high_neutron-5}}
        \caption{Vacancy Supersaturation profiles for normal and high dose neutron irradation with 5\% Production Bias}
        \label{figure:vacancy_supersaturation_neutron_5}
      \end{figure}
    \subsubsection{Sink Strengths}
    The grain boundary sink strengths are calculated by using the equation \ref{equation:sink_strength}. First of all the defect concentration profile found by MOOSE is validated by comparing to analytical result as shown in Fig.\ref{figure:concentrations_MOOSE_analytical}
      \begin{figure}[h!]
        \centering
        \includegraphics[scale=0.6]{concentration_profiles_MOOSE_Analytical_Neutron_0}
        \caption{Comparison of MOOSE results with analytical solution for a 1D spherical grain.\cite{heald1977}}
        \label{figure:concentrations_MOOSE_analytical}
      \end{figure}
      \begin{figure}[h!]  %Sink Strength - Neutron 1e-6 dpa/s - 0% Bias rate
        \centering
        \subfloat{\includegraphics[scale=0.6]{sink_strength_moose_neutron_0_k}}
        \qquad
        \subfloat{\includegraphics[scale=0.6]{sink_strength_moose_neutron_0_Z}}
        \caption{Sink Strengths for neutron irradiation with 0\% Production Bias}
        \label{figure:sink_strengths_neutron_0_1e-6}
      \end{figure}
      \begin{figure}[h!]  %Sink Strength - Neutron 1e-6 dpa/s - 5% Bias rate
        \centering
        \subfloat{\includegraphics[scale=0.6]{sink_strength_moose_neutron_5_k}}
        \qquad
        \subfloat{\includegraphics[scale=0.6]{sink_strength_moose_neutron_5_Z}}
        \caption{Sink Strengths for neutron irradation with 5\% Production Bias}
        \label{figure:sink_strengths_neutron_5_1e-6}
      \end{figure}

  \subsection{Ion Irradiation}
    \subsubsection{Concentrations}
      \begin{figure}[h!]  %Ion - 1e-3 dpa/s - %0 Bias rate
        \centering
        \subfloat{\includegraphics[scale=0.6]{interstitial_concentration_500-5000nm-ion-0}}
        \qquad
        \subfloat{\includegraphics[scale=0.6]{vacancy_concentration_500-5000nm-ion-0}}
        \caption{Concentration profiles for low dose ion irradation with 0\% Production Bias}
        \label{figure:concentrations_ion_0_1e-6}
      \end{figure}
      \begin{figure}[h!]  %Ion - 1e-6 dpa/s - %0 Bias rate
        \centering
        \subfloat{\includegraphics[scale=0.6]{interstitial_concentration_500-5000nm-low_ion-0}}
        \qquad
        \subfloat{\includegraphics[scale=0.6]{vacancy_concentration_500-5000nm-low_ion-0}}
        \caption{Concentration profiles for ion irradiation with 0\% Production Bias}
        \label{figure:concentrations_ion_0_1e-3}
      \end{figure}
      \begin{figure}[h!]  %Ion - 1e-3 dpa/s - %5 Bias rate
        \centering
        \subfloat{\includegraphics[scale=0.6]{interstitial_concentration_500-5000nm-ion-5}}
        \qquad
        \subfloat{\includegraphics[scale=0.6]{vacancy_concentration_500-5000nm-ion-5}}
        \caption{Concentration profiles for low dose ion irradation with 5\% Production Bias}
        \label{figure:concentrations_ion_5_1e-6}
      \end{figure}
      \begin{figure}[h!]  %Ion - 1e-6 dpa/s - %5 Bias rate
        \centering
        \subfloat{\includegraphics[scale=0.6]{interstitial_concentration_500-5000nm-low_ion-5}}
        \qquad
        \subfloat{\includegraphics[scale=0.6]{vacancy_concentration_500-5000nm-low_ion-5}}
        \caption{Concentration profiles for ion irradation with 5\% Production Bias}
        \label{figure:concentrations_ion_5_1e-3}
      \end{figure}
      \begin{figure}[h!]  %Ion - %5 Bias rate
        \centering
        \subfloat{\includegraphics[scale=0.6]{super_saturation_500-5000nm-ion-5}}
        \qquad
        \subfloat{\includegraphics[scale=0.6]{super_saturation_500-5000nm-low_ion-5}}
        \caption{Vacancy Supersaturation profiles for low dose and ion irradation with 5\% Production Bias}
        \label{figure:vacancy_supersaturation_ion_5}
      \end{figure}

>>>>

  \subsection{Neutron Irradiation} \hspace{10pt}
  Neutrons have an energy spectrum that varies a couple of orders of magnitude. This makes defect generation possible at different energies. Also, the high penetration depth of neutrons allow them travel through material corresponding to their energy and end up with an uniform or flat-like defect profiles.
    \subsubsection{Concentrations} \hspace{10pt}
      \begin{figure}[h!]  %Neutron - 1e-6 dpa/s - %0 Bias rate
        \centering
        \subfloat{\includegraphics[scale=0.6]{interstitial_concentration_500-5000nm-neutron-0}}
        \qquad
        \subfloat{\includegraphics[scale=0.6]{vacancy_concentration_500-5000nm-neutron-0}}
        \caption{Concentration profiles for neutron irradation with 0\% Production Bias}
        \label{figure:concentrations_neutron_0_1e-6}
      \end{figure}
      \begin{figure}[h!]  %Neutron - 1e-3 dpa/s - %0 Bias rate
        \centering
        \subfloat{\includegraphics[scale=0.6]{interstitial_concentration_500-5000nm-high_neutron-0}}
        \qquad
        \subfloat{\includegraphics[scale=0.6]{vacancy_concentration_500-5000nm-high_neutron-0}}
        \caption{Concentration profiles for high dose neutron irradation with 0\% Production Bias}
        \label{figure:concentrations_neutron_0_1e-3}
      \end{figure}
      \begin{figure}[h!]  %Neutron - 1e-6 dpa/s - %5 Bias rate
        \centering
        \subfloat{\includegraphics[scale=0.6]{interstitial_concentration_500-5000nm-neutron-5}}
        \qquad
        \subfloat{\includegraphics[scale=0.6]{vacancy_concentration_500-5000nm-neutron-5}}
        \caption{Concentration profiles for neutron irradation with 5\% Production Bias}
        \label{figure:concentrations_neutron_5_1e-6}
      \end{figure}
      \begin{figure}[h!]  %Neutron - 1e-3 dpa/s - %5 Bias rate
        \centering
        \subfloat{\includegraphics[scale=0.6]{interstitial_concentration_500-5000nm-high_neutron-5}}
        \qquad
        \subfloat{\includegraphics[scale=0.6]{vacancy_concentration_500-5000nm-high_neutron-5}}
        \caption{Concentration profiles for high dose neutron irradation with 5\% Production Bias}
        \label{figure:concentrations_neutron_5_1e-3}
      \end{figure}
      \begin{figure}[h!]  %Nuetron - Vacancy Supersaturation - 5% Bias
        \centering
        \subfloat{\includegraphics[scale=0.6]{super_saturation_500-5000nm-neutron-5}}
        \qquad
        \subfloat{\includegraphics[scale=0.6]{super_saturation_500-5000nm-high_neutron-5}}
        \caption{Vacancy Supersaturation profiles for normal and high dose neutron irradation with 5\% Production Bias}
        \label{figure:vacancy_supersaturation_neutron_5}
      \end{figure}
    \subsubsection{Sink Strengths}
    The grain boundary sink strengths are calculated by using the equation \ref{equation:sink_strength}. First of all the defect concentration profile found by MOOSE is validated by comparing to analytical result as shown in Fig.\ref{figure:concentrations_MOOSE_analytical}
      \begin{figure}[h!]
        \centering
        \includegraphics[scale=0.6]{concentration_profiles_MOOSE_Analytical_Neutron_0}
        \caption{Comparison of MOOSE results with analytical solution for a 1D spherical grain.\cite{heald1977}}
        \label{figure:concentrations_MOOSE_analytical}
      \end{figure}
      \begin{figure}[h!]  %Sink Strength - Neutron 1e-6 dpa/s - 0% Bias rate
        \centering
        \subfloat{\includegraphics[scale=0.6]{sink_strength_moose_neutron_0_k}}
        \qquad
        \subfloat{\includegraphics[scale=0.6]{sink_strength_moose_neutron_0_Z}}
        \caption{Sink Strengths for neutron irradiation with 0\% Production Bias}
        \label{figure:sink_strengths_neutron_0_1e-6}
      \end{figure}
      \begin{figure}[h!]  %Sink Strength - Neutron 1e-6 dpa/s - 5% Bias rate
        \centering
        \subfloat{\includegraphics[scale=0.6]{sink_strength_moose_neutron_5_k}}
        \qquad
        \subfloat{\includegraphics[scale=0.6]{sink_strength_moose_neutron_5_Z}}
        \caption{Sink Strengths for neutron irradation with 5\% Production Bias}
        \label{figure:sink_strengths_neutron_5_1e-6}
      \end{figure}

  \subsection{Ion Irradiation} \hspace{10pt}
  Unlike neutrons, ions have relatively narrow energy channel width which is almost monoenergetic. Furtmermore, they cannot penetrate through material a lot because of high energy loss in collisions. These characteristic causes a non-uniform defect profiles.
    \subsubsection{Concentrations}
      \begin{figure}[h!]  %Ion - 1e-3 dpa/s - %0 Bias rate
        \centering
        \subfloat{\includegraphics[scale=0.6]{interstitial_concentration_500-5000nm-ion-0}}
        \qquad
        \subfloat{\includegraphics[scale=0.6]{vacancy_concentration_500-5000nm-ion-0}}
        \caption{Concentration profiles for low dose ion irradation with 0\% Production Bias}
        \label{figure:concentrations_ion_0_1e-6}
      \end{figure}
      \begin{figure}[h!]  %Ion - 1e-6 dpa/s - %0 Bias rate
        \centering
        \subfloat{\includegraphics[scale=0.6]{interstitial_concentration_500-5000nm-low_ion-0}}
        \qquad
        \subfloat{\includegraphics[scale=0.6]{vacancy_concentration_500-5000nm-low_ion-0}}
        \caption{Concentration profiles for ion irradiation with 0\% Production Bias}
        \label{figure:concentrations_ion_0_1e-3}
      \end{figure}
      \begin{figure}[h!]  %Ion - 1e-3 dpa/s - %5 Bias rate
        \centering
        \subfloat{\includegraphics[scale=0.6]{interstitial_concentration_500-5000nm-ion-5}}
        \qquad
        \subfloat{\includegraphics[scale=0.6]{vacancy_concentration_500-5000nm-ion-5}}
        \caption{Concentration profiles for low dose ion irradation with 5\% Production Bias}
        \label{figure:concentrations_ion_5_1e-6}
      \end{figure}
      \begin{figure}[h!]  %Ion - 1e-6 dpa/s - %5 Bias rate
        \centering
        \subfloat{\includegraphics[scale=0.6]{interstitial_concentration_500-5000nm-low_ion-5}}
        \qquad
        \subfloat{\includegraphics[scale=0.6]{vacancy_concentration_500-5000nm-low_ion-5}}
        \caption{Concentration profiles for ion irradation with 5\% Production Bias}
        \label{figure:concentrations_ion_5_1e-3}
      \end{figure}
      \begin{figure}[h!]  %Ion - %5 Bias rate
        \centering
        \subfloat{\includegraphics[scale=0.6]{super_saturation_500-5000nm-ion-5}}
        \qquad
        \subfloat{\includegraphics[scale=0.6]{super_saturation_500-5000nm-low_ion-5}}
        \caption{Vacancy Supersaturation profiles for low dose and ion irradation with 5\% Production Bias}
        \label{figure:vacancy_supersaturation_ion_5}
      \end{figure}
